---
title: "Assessing rank stability across docking scenarios"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Assessing rank stability across docking scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(dockclaimR)
```

## Purpose and boundary

This vignette shows how `dockclaimR` summarizes a *prespecified* ranking
criterion across several docking scenarios. The values below are synthetic;
they are included only to demonstrate the software and are not molecular
docking results.

A stable rank does not establish binding, activity, selectivity, toxicity, or
experimental usefulness. It is evidence only about the supplied computational
ranking under the declared scenario set.

## Record provenance first

Before an analysis, complete and validate a manifest. Values here are
placeholders solely for this synthetic demonstration.

```{r}
manifest <- docking_manifest_template()
manifest[] <- "synthetic-example"
manifest$score_direction <- "lower"
validate_docking_manifest(manifest)
```

```{r}
runs <- data.frame(
  ligand_id = rep(c("candidate_a", "candidate_b", "candidate_c"), 3),
  scenario_id = rep(c("seed_1", "seed_2", "alternate_receptor"), each = 3),
  score = c(-8.1, -7.4, -6.8, -7.8, -8.3, -6.5, -7.7, -8.0, -6.6)
)

ranked <- rank_docking_runs(runs)
ranked
```

## Top-k stability

Here, `top_k = 1` means that a ligand must be ranked first inside a scenario.
The threshold is set before interpreting the result.

```{r}
stability <- summarise_top_k_stability(runs, top_k = 1)
stability

claims <- assess_top_k_stability(stability, threshold = 0.90)
claims
```

`candidate_a` and `candidate_b` each lead in only one of three scenarios.
Neither therefore passes a 90% top-1 stability criterion. This is a useful
negative result: it signals that the proposed prioritization is sensitive to
the scenario definition and should not be condensed into a single definitive
ranking.

## Using real docking outputs responsibly

Before using this workflow with real outputs, retain a manifest containing at
least the engine and version, receptor identifier, search-space identifier,
score direction, ligand preparation, random-seed policy, and each
scenario-defining choice. Keep scores in their native scale; `dockclaimR`
compares ranks within scenarios rather than pooling incompatible score scales.
